### 2023-12-16 documentation/thesis/thesis_document.tex
more thesis

@@

The graphic \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the control
\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
sensor opposite the Control \gls{pc}, even if there are several proxy
instances behind it.

@@

The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  [Y/n] [y]: 
\end{lstlisting}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock (see chapter \ref{sensor-syncronsisation}). However, this
no longer works for long distances and the syncronisation must be made
via the network connection.

@@

@@

@@

In order to provide comprehensive documentation for the user, the source
code was documented using
Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}.
This includes, among other things:

\begin{itemize}
\tightlist
\item
  Function description
\item
  Input parameters - \passthrough{\lstinline!param!} and
  \passthrough{\lstinline!type!}
\item
  Return value - \passthrough{\lstinline!returns!},
  \passthrough{\lstinline!rtype!}
\end{itemize}

@@

        :returns: returns the filepath of the generated .png image file
        :rtype: str
        """

@@

@@

\cite{ReadTheDocs}

\cite{MagneticReadoutProcessingReadTheDocs}

\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}

\hypertarget{tests}{%
\subsection{Tests}\label{tests}}

>>>>

\hypertarget{usecases}{%
\chapter{Usecases}\label{usecases}}

@@

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the control
\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
sensor opposite the Control \gls{pc}, even if there are several proxy
instances behind it.

@@

The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  Proxy instance [y/N] [n]: 
\end{lstlisting}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock (see chapter \ref{sensor-syncronsisation}). this no longer
works for long distances and the syncronisation must be made via the
network connection.

@@

\ref{example_measurement_analysis_pipeline.png}

@@

\hypertarget{tests}{%
\section{Tests}\label{tests}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png}
\caption{MRP library test results for different submodules executed in
PyCharm \gls{ide}
\label{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png}}
\end{figure}

Software tests in libraries offer numerous advantages for improving
quality and efficiency. Firstly, they enable the identification of
errors and vulnerabilities before software is published as a new
version. This significantly improves the reliability of library
applications. Tests also ensures consistent and reliable performance,
which is particularly important when libraries are used by different
users and for different usecases.

During the development of the library, test cases were also created for
all important functionalities and use cases. The test framework
\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
purpose, as it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. Since
all intended use cases were mapped using the test cases created, the
code of the test cases could later be used in slightly simplified
variants as examples for the documentation.

\begin{lstlisting}[language=Python]
# $ cat test_mrpreading.py
class TestMPRReading(unittest.TestCase):
    # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
    def setUp(self) -> None:
        self.import_export_test_folderpath: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
        self.import_export_test_filepath:str = os.path.join(self.import_export_test_folderpath, "tmp")

    def test_matrix(self):
        reading: MRPReading = MRPSimulation.MRPSimulation.generate_reading()
        matrix: np.ndarray = reading.to_numpy_matrix()
        n_phi: float = reading.measurement_config.n_phi
        n_theta: float = reading.measurement_config.n_theta
        # CHECK MATRIX SHAPE
        self.assertTrue(matrix.shape != (n_theta, ) and len(matrix.shape) <= n_phi)

    def test_export_reading(self) -> None:
        reading: MRPReading = self.test_reading_init()
        self.assertIsNotNone(reading)
        # EXPORT READING TO A FILE
        reading.dump_to_file(self.import_export_test_filepath)

    def test_import_reading(self):
        # CREATE EMPTY READING
        reading_imported:MRPReading = MRPReading.MRPReading(None)
        # LOAD READING FROM FILE
        reading_imported.load_from_file(self.import_export_test_filepath)
        # CHECK IF ENTRIES ARE POPULATED
        self.assertIsNotNone(reading_imported.additional_data)
        self.assertIsNotNone(reading_imported.data)

if __name__ == '__main__':
    unittest.main()
\end{lstlisting}

One problem, however, is the parts of the library that require direct
access to external hardware. These are, for example, the
\passthrough{\lstinline!MRPHal!} and
\passthrough{\lstinline!MRPHalRest!} modules, which are required to read
out sensors connected via the network. Two different approaches were
used here. In the case of local development, the test runs were carried
out on a \gls{pc} that can reach the network hardware and thus the test
run could be carried out with real data.

In the other scenario, the tests are to be carried out before a new
release in the repository on the basis of
\passthrough{\lstinline!Github Actions!}\cite{GithubActions}. Here
there is the possibility to host local runner software, which then has
access to the hardware, but then a \gls{pc} must be permanently
available for this task. Instead, the hardware sensors were simulated by
software and executed via virtualisation on the systems provided by
\passthrough{\lstinline!Github Actions!}\cite{GithubActions}.

@@

In order to provide comprehensive documentation for the enduser, the
source code was documented using
Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}
and the Python3.5 type annotations:

\begin{itemize}
\tightlist
\item
  Function description
\item
  Input parameters - using \passthrough{\lstinline!param!} and
  \passthrough{\lstinline!type!}
\item
  Return value - using \passthrough{\lstinline!returns!},
  \passthrough{\lstinline!rtype!}
\end{itemize}

@@

        :returns: returns the abs filepath of the generated .png image file
        :rtype: str
        """

@@

The use of type annotations also simplifies further development, as
modern \gls{ide}s can more reliably display possible methods to the user
as an assistance.

@@

Once the finished documentation has been generated from static
\gls{html} files, it is stored in the project repository. Another
publication option is to host the documentation via online services such
as \passthrough{\lstinline!ReadTheDocs!}\cite{ReadTheDocs}, where
users can make documentation for typical software projects available to
others.

The documentation has also been uploaded for
\passthrough{\lstinline!ReadTheDocs!}\cite{MagneticReadoutProcessingReadTheDocs}
and linked in the repository and on the overview
page\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
on \passthrough{\lstinline!PyPi!}.

The process of creating and publishing the documentation has been
automated using
\passthrough{\lstinline!GitHub Actions!}\cite{GithubActions}, so
that it is always automatically kept up to date with new features.
